---
title: "funnyPackage"
author: "liuc"
date: '2022-03-01'
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## funnyPackage

此处记录碰到的一些有意思、有用的各种R package。


### DataEditR

https://dillonhammill.github.io/DataEditR/
一个可以交互修改整理数据的R包。
```{r}
data_edit(mtcars,
          viewer = "browser")
```



### ProjectTemplate

ProjectTemplate is a system for automating the thoughtless parts of a data analysis project。
不过感觉很多时候选择RStudio自带的用起来就很舒服。


### compareGroups

一个用于对比因变量和自变量关系的包.


### datapasta

将复制的数据变成dataframe等格式。


### ggThemeAssist

免代码调节ggplot的细节参数，比如字体，背景颜色


### livecode
局域网网页直播写代码



### 2022-03-4

```{r}
# simpr
# simpr provides a general, simple, and tidyverse-friendly framework for generating simulated data, fitting models on simulations, and tidying model results.


# biodosetools
# 剂量依赖的计算方法，不是很搞得清它是做什么的


# interpretCI
# 计算并展示CI的包，不过desctools已经挺好用的了吧


# https://github.com/adayim/forestploter
# 这个绘制森林图的包似乎和用过的一个很类似


```


### summarytools

一个对数据进行summary的工具集合


### marginaleffects

marginaleffects is an R package to compute and plot adjusted predictions, marginal effects, contrasts, and marginal means for a wide variety of models.


# R for pharma
```{r}
# https://pharmaverse.org/nonpharma/ 有挺多的R包推荐

# visR  看样子以后做生存分析需要这种了
# The goal of visR is to enable fit-for-purpose, reusable clinical and medical research focused visualizations and tables with sensible defaults and based on sound graphical principles.

# pharmaverse https://pharmaverse.org/
#



```




### grafify

一个方便的R绘图包，在emmeans绘制时比较的方便。


### https://r-sassy.org/
The sassy system was built for these programmers. The system offers a set of packages that make programming in R much more similar to programming in SAS®.

在R markdown中也可以跑SAS




